Legends for supplementary material

### 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
editted legend for clarity

**Supplementary Figure 3. Heatmaps illustrating the variable reduction.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines. Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red. Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance). The yellow lines separate each of the three predictor types.

>>>>

**Supplementary Figure 3. Heatmaps illustrating which features were reduced using Elastic-Net regularization.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines. Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red. Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance). The yellow lines separate each of the three predictor types (overlap counts, overlap percents, and distance types respectively).
